% !TEX program = xelatex

% Set the directory for input files, useful for organizing larger projects
\makeatletter
\def\input@path{{tex/}}
\makeatother

% Document class and options
\documentclass[11pt, letterpaper]{awesome-cv}

%%% Packages %%%

% Hyperlink setup for interactive PDF elements
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=cyan
}

% Enables multicolumn layouts, particularly useful in sections like Skills
\usepackage{multicol}

% Customizes list spacing. Reducing spacing for compact presentation
\usepackage{enumitem}
\setlist{nosep}

% Customizing document margins
\geometry{margin=0.5in}

% Setting the directory for font files
\fontdir[fonts/]

% Color definition for theme
% Dark grey color chosen for a professional look
\definecolor{awesome}{HTML}{414141}

%%% Personal Information %%%
% This section contains your personal information
\name{Nicholas}{Nadeau}
\address{Montréal, Canada}
\mobile{+1-514-573-5620}
\email{nicholas.nadeau@gmail.com}
\position{CTO, Professional Engineer (P.Eng.), Doctor of Philosophy (Ph.D.)}

% Social Links
\homepage{nicholasnadeau.com}
\github{EngNadeau}
\googlescholar{Soo4zroAAAAJ&hl}{Nicholas A. Nadeau}

% Footer settings
\makecvfooter{\today}{}{\thepage}

%%% Document Content %%%
\begin{document}

% Header
\makecvheader

% Work Experience Section
\cvsection{Work}
\begin{cventries}
    % Each \cventry has specific details related to a job position
    % Format: \cventry{job title}{organization}{location}{date range}{job details}

    \cventry{Founder}{Nadeau Innovations}{Montréal, Canada}{2017 - Present}{
        \begin{cvitems}
            \item{Offered fractional CTO services to advance AI/ML and robotics in startups and growth companies.}
            \item{Assisted executive teams with strategic planning and roadmaps.}
            \item{Coached managers and team leads on agile project execution and operations.}
        \end{cvitems}
    }

    \cventry
    {CTO}
    {Halodi Robotics}
    {Montréal, Canada \& Oslo, Norway}
    {2021 - 2023}
    {
        \begin{cvitems}
            \item{Developed a new humanoid robot for security guarding and expanded the team to 50+ employees across 4 countries.}
            \item{Secured the largest contract ever for humanoid robots with ADT Commercial (140 robots), raised \$10M in Series A funding, and raised \$24M in Series A2 with OpenAI.}
            \item{Managed software development, architecture design, and internal infrastructure implementation.}
        \end{cvitems}
    }

    \cventry
    {Advisor}
    {BRIDGR}
    {Montréal, Canada}
    {2020 - }
    {
        \begin{cvitems}
            \item{Provided expertise on team growth, architecture, and special projects in robotics and Industry 4.0.}
            \item{Mentored through the Techstars AI Montréal accelerator.}
            \item{Facilitated critical introductions for business development.}
        \end{cvitems}
    }

    \cventry
    {Engineering Manager}
    {AON3D}
    {Montréal, Canada}
    {2018 - 2021}
    {
        \begin{cvitems}
            \item{Headed engineering and secured \$11.5M Series A funding for high-performance 3D printing systems.}
            \item{Directed software and hardware development, product strategy, and certification efforts.}
            \item{Managed SR\&ED Tax Incentive Program, securing \$300K+ in tax refunds.}
        \end{cvitems}
    }


    \cventry
    {Technology Advisor to the CEO}
    {YPC Technologies}
    {Montréal, Canada}
    {2017 - 2018}
    {
        \begin{cvitems}
            \item{Advised CEO during startup accelerator, resulting in \$1.8M seed funding from top investors.}
            \item{Led engineering team for robotics and software design for FounderFuel Demo Day.}
            \item{Collaborated on strategy and execution with the CEO.}
        \end{cvitems}
    }

    \cventry
    {R\&D Engineer}
    {Rogue Research Inc.}
    {Montréal, Canada}
    {2011 - 2018}
    {
        \begin{cvitems}
            \item{Developed a novel robotic veterinary neurosurgery system, including algorithms and hardware design.}
            \item{Created biomedical devices for TMS, NIRS, DBS, and image-based neuronavigation.}
            \item{Contributed to advancements in computer vision and neuroscience.}
        \end{cvitems}
    }
\end{cventries}

% Education Section
\cvsection{Education}
\begin{cventries}
    \cventry
    {Ph.D. - Precision and Collaborative Robotics}
    {École de technologie supérieure}
    {Montréal, Canada}
    {2014 - 2019}
    {
        \begin{cvitems}
            \item{Thesis: \href{https://www.nicholasnadeau.com/publication/nadeau-2019-towards/}{Towards the Development of Safe, Collaborative Robotic Freehand Ultrasound}}
            \item{Development of \href{https://www.nicholasnadeau.com/talk/hardware-in-the-loop-training-robot-contact-in-an-unstructured-environment/}{AI/ML models and algorithms} for physical human-robot interaction, \href{https://www.nicholasnadeau.com/publication/nadeau-2018-evolutionary/}{controller tuning}, and \href{https://www.nicholasnadeau.com/publication/nadeau-2019-impedance/}{robot calibration}.}
            \item{Creator of \href{https://github.com/EngNadeau/pybotics}{\textit{Pybotics}}, a \href{https://joss.theoj.org/papers/10.21105/joss.01738}{published} open-source Python toolbox for robotics calibration, kinematics, ML/AI, and optimization.}
        \end{cvitems}
    }

    \cventry
    {B.Eng. - Mechanical Engineering, Biomedical Engineering Minor}
    {McGill University}
    {Montréal, Canada}
    {2010 - 2014}
    {
        \begin{cvitems}
        \end{cvitems}
    }
\end{cventries}

% Skills Section
\cvsection{Skills \& Certifications}
\begin{cvskills}
    \cvskill
    {Certifications}
    {
        Associate Value Specialist (SAVE International),
        Open Water Diver (PADI),
        Professional Engineer (Ordre des ingénieurs du Québec)
    }

    \cvskill
    {Engineering}
    {
        Confluence,
        GitHub,
        GitLab,
        Jira,
        KiCAD,
        SOLIDWORKS
    }

    \cvskill
    {Software}
    {
        Balena,
        CMake,
        Docker,
        Flask,
        Gradle,
        gRPC,
        Linux,
        Make,
        PyTorch,
        REST API,
        ROS,
        TensorFlow,
        Yocto
    }

    \cvskill
    {Programming}
    {
        C/C++,
        Java,
        LaTeX,
        Node.js,
        Python
    }

    \cvskill
    {Languages}
    {
        English,
        French
    }
\end{cvskills}

% Publications Section
\cvsection{Recent Publications}
\begin{cvhonors}
    \cvhonor
    {Improved Test Methods for Polymer AM Inter-Layer Weld Strength and Filament Mechanical Properties}
    {Richard G. Cole, Kazem Fayazbakhsh, Abraham Avalos, Nicholas A. Nadeau. ASTM International Conference on Additive Manufacturing (ICAM).}
    {}
    {2020}

    \cvhonor
    {Towards the development of safe, collaborative robotic freehand ultrasound}
    {Nicholas A. Nadeau. École de technologie supérieure.}
    {}
    {2019}

    \cvhonor
    {Pybotics: Python Toolbox for Robotics}
    {Nicholas A. Nadeau. The Journal of Open Source Software.}
    {}
    {2019}

    \cvhonor
    {Impedance Control Self-Calibration of a Collaborative Robot Using Kinematic Coupling}
    {Nicholas A. Nadeau, Ilian A. Bonev. MDPI Robotics.}
    {}
    {2019}

    \cvhonor
    {Evolutionary Motion Control Optimization in Physical Human-Robot Interaction}
    {Nicholas A. Nadeau, Ilian A. Bonev. IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS).}
    {}
    {2018}

    \cvhonor
    {An Extrinsic Dexterity Approach to the IROS 2018 Fan Robotic Challenge Modality B}
    {Jennifer Kwiatkowski, Jean-Philippe Roberge, Nicholas A. Nadeau, Louis L'Écuyer-Lapierre, Vincent Duchaine. IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS).}
    {}
    {2018}

    \cvhonor
    {Characterization of a robotic micro-surgical system for small-animal neurosurgery}
    {Nicholas A. Nadeau, Alexandru Ciobanu, Fred Lamer, Mathieu Coursolle, Sean McBride, Stephen Frey, Roch Comeau. Society for Neuroscience.}
    {}
    {2017}
\end{cvhonors}

% Talks Section
\cvsection{Recent Talks}
\begin{cvhonors}
    \cvhonor
    {The Applications of Pybotics}
    {Seattle Robotics Society}
    {}
    {2022-10}

    \cvhonor
    {Applying Key Hardware Design Considerations}
    {Design to Product Podcast}
    {}
    {2022-08}

    \cvhonor
    {Careers in Robotics}
    {Dallas ISD STEM Expo}
    {}
    {2022-01}

    \cvhonor
    {Let's talk robotics with Dr. Nicholas Nadeau!}
    {Let’s Talk Robotics Podcast}
    {}
    {2021-10}

    \cvhonor
    {Safe and Capable Robots}
    {IEEE-EMBS Robotics Webinar}
    {}
    {2021-10}

    \cvhonor
    {Hiring for Inclusive Robotics}
    {Silicon Valley Robotics - Society, Robots, and Us}
    {}
    {2021-04}

    \cvhonor
    {Hardware in the Loop: Training Robot Contact in an Unstructured Environment}
    {Montréal-Python 85}
    {}
    {2021-04}

    \cvhonor
    {Making Materials Matter}
    {Dyndrite Developer Conference 2020}
    {}
    {2020-04}

    \cvhonor
    {Evolutionary Motion Control Optimization in Physical Human-Robot Interaction}
    {2018 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}
    {}
    {2018-10}

    \cvhonor
    {Calibrating Robots with Python}
    {PyCon Canada 2017}
    {}
    {2017-11}
\end{cvhonors}

% Volunteer & Committees Section
\cvsection{Volunteer \& Committees}
\begin{cvhonors}
    \cvhonor
    {Startup Mentor}
    {Next AI}
    {}
    {2022}

    \cvhonor
    {Startup Mentor}
    {Creative Destruction Lab (CDL)}
    {}
    {2022}

    \cvhonor
    {Technical Committee ISO/TC 299 - Robotics}
    {Standards Council of Canada Mirror Committee}
    {}
    {2021}

    \cvhonor
    {Mentor}
    {Techstars Montréal AI Accelerator}
    {}
    {2020}

    \cvhonor
    {Mentor}
    {FounderFuel Startup Accelerator}
    {}
    {2020}

    \cvhonor
    {Member of Technical Expert Panel \& Mentor}
    {Code Life Ventilator Challenge for COVID-19}
    {}
    {2020}

    \cvhonor
    {Reviewer}
    {Sensors, MDPI}
    {}
    {2020}

    \cvhonor
    {Reviewer}
    {Journal of Applied Mathematical Modelling}
    {}
    {2019}

    \cvhonor
    {Reviewer}
    {International Journal of Advanced Robotic Systems (IJARS)}
    {}
    {2019}

    \cvhonor
    {Committee F42 on Additive Manufacturing Technologies}
    {ASTM International}
    {}
    {2018}

    \cvhonor
    {Reviewer}
    {The Journal of Open Source Software (JOSS)}
    {}
    {2018}
\end{cvhonors}

\end{document}
