% !TEX program = xelatex
\documentclass[11pt, letterpaper]{awesome-cv}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\geometry{margin=0.5in}
\fontdir[fonts/]

% dark grey, https://www.color-hex.com/color/414141
\definecolor{awesome}{HTML}{414141}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% awesome cv data
\name{Nicholas}{Nadeau}
\address{Montréal, Canada}
\mobile{+1-514-573-5620}
\email{nicholas.nadeau@gmail.com}
\position{
Professional Engineer (P.Eng.),
Doctor of Philosophy (Ph.D.)
}
\homepage{www.nicholasnadeau.me}
\github{nnadeau}
\twitter{EngNadeau}
\makecvfooter{\today}{}{\thepage}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% The company being applied to
\recipient
{XXX Recruitment Team}
{XXX Inc.\\STREET\\CITY, STATE ZIP}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for POSITION}
% How the letter is opened
\letteropening{Dear XXX,}
% How the letter is closed
\letterclosing{Cheers,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\begin{document}

% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
{\today}
{Nicholas Nadeau}
{}

% Print the title with above letter informations
\makelettertitle

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\begin{cvletter}

    \lettersection{About Me}

    I have has spent the last decade creating unique technologies at the intersection of hardware and software for the biomedical, cognitive neuroscience, robotics, and additive manufacturing domains.
    Notably, my Ph.D. combined machine learning and collaborative robotics to develop methods for safe robotic freehand medical ultrasound.
    Currently, I am an executive and the head of engineering at AON3D where I lead design, development, and R\&D in both software and hardware to drive product innovation.
    In my spare time, I mentor local startups, principally through the FounderFuel and Techstars Montréal AI accelerators.

    \lettersection{Why XXX?}

    XXX has been on my radar as a next step in my career, where I can innovate with a long-term vision instead of just short-term products.
    I admire the ambitious ideas that are explored and developed, and the celebration of failure, iteration, and creativity.
    The integration of robotics, AI, and people are especially interesting considering my Ph.D. thesis' focus on exploring collaborative robotics and physical human-robot interaction in medical contexts to improve healthcare professionals' quality of life and efficacy.
    I am very excited for an integrated future, and I believe our missions and visions are aligned.

    \lettersection{Why Me?}

    Bridging the gap between R\&D and commercial products has been my primary career focus over the past decade, with many of my projects starting with a stakeholder asking "can we do this?".
    I am a "full-stack" hardware engineer, having jumped between mechanical, electrical, biomedical, robotics, and software engineering roles.
    While I am most at home in an R\&D lab, my recent years as an executive and engineering leader has given me the opportunity build an outstanding multidisciplinary team, develop successful product development processes, and deliver value to our users.

    As a bonus, I organize jubilant holiday parties and devious D\&D campaigns for my team, as I see their happiness and success as my biggest pride.

\end{cvletter}

\makeletterclosing

\end{document}
