\documentclass[11pt, letterpaper]{awesome-cv}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% multicolumn list
\usepackage{multicol}   

% list spacing
\usepackage{enumitem}   
\setlist{nosep} % list spacing

\geometry{margin=0.5in}
\fontdir[fonts/]

% dark grey, https://www.color-hex.com/color/414141
\definecolor{awesome}{HTML}{414141}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% awesome cv data
\name{Nicholas}{Nadeau}
\address{Montréal, Canada}
\mobile{+1-514-573-5620}
\email{nicholas.nadeau@gmail.com}
\position{
Professional Engineer (P.Eng.), 
Associate Value Specialist (AVS)
}
\homepage{www.nicholasnadeau.me}
\github{nnadeau}
\twitter{EngNadeau}
\makecvfooter{\today}{}{\thepage}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\begin{document}
\makecvheader

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\cvsection{Education}
\begin{cventries}

\cventry
{PhD - Precision and Collaborative Robotics}
{École de technologie supérieure}
{Montréal, Canada}
{2014 - }
{
\begin{cvitems} 
\item{Thesis: Towards the Development of Safe, Collaborative Robotic Freehand Ultrasound}
\item{Created machine learning models and genetic algorithms for physical human-robot interaction.}
\item{Invented a novel, robust, low-cost robot calibration platform.}
\end{cvitems}
}

\cventry
{B.Eng. - Mechanical Engineering, Biomedical Engineering Minor}
{McGill University}
{Montréal, Canada}
{2010 - 2014}
{
\begin{cvitems}
\end{cvitems}
}

\cventry
{DEC - Honours Health Science}
{Dawson College}
{Montréal, Canada}
{2008 - 2010}
{
\begin{cvitems} 
\end{cvitems}
}

\end{cventries}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\cvsection{Work}
\begin{cventries}

\cventry
{Engineering Manager}
{AON3D}
{Montréal, Canada}
{2019 - }
{
\begin{cvitems} 
\item{Oversee and drive the design, development, testing, and deployment of innovative solutions for challenging problems in the additive manufacturing domain.}
\item{Ensure robust, scalable, reusable, efficient, production-quality software and hardware is being delivered to the organization.}
\item{Usher and evangelize adoption of engineering best-practices and methodology.}
\item{Set the roadmap, drive detailed planning, and ensure execution of deliverables for a medium sized team.}
\item{Mentor and help bringing up of new team members, help with interviewing and hiring of new team members, ensure technical development of team.}
\item{Research and incorporate emerging software infrastructures, tools, and technologies.}
\end{cvitems}
}

\cventry
{Senior R&D Engineer}
{AON3D}
{Montréal, Canada}
{2018 - 2019}
{
\begin{cvitems} 
\item{Responsible for innovation and technology development to drive 10x revenue.}
\item{Introduced automated data collection framework to help drive business and engineering decisions.}
\item{Engineering ScrumMaster, responsible for ensuring the team has everything they need to deliver value.}
\end{cvitems}
}

\cventry
{Engineering & Technology Consultant}
{YPC Technologies}
{Montréal, Canada}
{2017 - 2018}
{
\begin{cvitems} 
\item{Advised CEO throughout FounderFuel startup accelerator in order to go to market and raise seed capital.}
\item{Led a team of engineers and directed robotics and software design, development, and implementation.}
\item{Recommended long-term approach to strategic suppliers and technologies with the aim of optimizing operations and delivering savings.}
\end{cvitems}
}

\cventry
{R&D Engineer}
{Rogue Research Inc.}
{Montréal, Canada}
{2011 - 2018}
{
\begin{cvitems} 
\item{Responsible for mechanical research, design, and development of brain imaging and robotic products.}
\item{Developed trajectory generation algorithms (C++) for collaborative veterinary neurosurgery.}
\item{Created thermal models (Python) for transcranial magnetic stimulation coils.}
\end{cvitems}
}

\end{cventries}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\cvsection{Volunteer}
\begin{cventries}
\cventry{Reviewer}{Applied Mathematical Modelling}{}{2019 - }{}
\cventry{Reviewer}{International Journal of Advanced Robotic Systems (IJARS)}{}{2019 - }{}
\cventry{Reviewer}{The Journal of Open Source Software (JOSS)}{}{2018 - }{}
\cventry{Communications Administrator}{Interaction du quartier Peter-McGill}{Montréal, Canada}{2013 - 2014}{}
\cventry{Discover McGill and Orientation Week Leader}{McGill University}{Montréal, Canada}{2011 - 2014}{}
\cventry{Treasurer and Communications Administrator}{Forum Jeunesse Centre-ville}{Montréal, Canada}{2012 - 2013}{}
\cventry{Volunteer Math and Science Teacher}{Innovation Jeunes}{Montréal, Canada}{2009 - 2011}{}
\end{cventries}

\cvsection{Publications}
\begin{cventries}

\cventry
{Nicholas A. Nadeau, Ilian A. Bonev. Robotics.}
{Impedance Control Self-Calibration of a Collaborative Robot Using Kinematic Coupling }
{}
{2019}
{}

\cventry
{Nicholas A. Nadeau, Ilian A. Bonev. IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS).}
{Evolutionary Motion Control Optimization in Physical Human-Robot Interaction}
{}
{2018}
{}

\cventry
{Jennifer Kwiatkowski, Jean-Philippe Roberge, Nicholas A. Nadeau, Louis L'Écuyer-Lapierre, Vincent Duchaine. IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS).}
{An Extrinsic Dexterity Approach to the IROS 2018 Fan Robotic Challenge Modality B}
{}
{2018}
{}

\cventry
{Nicholas A. Nadeau, Alexandru Ciobanu, Fred Lamer, Mathieu Coursolle, Sean McBride, Stephen Frey, Roch Comeau. Society for Neuroscience.}
{Characterization of a robotic micro-surgical system for small-animal neurosurgery}
{}
{2017}
{}

\end{cventries}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\cvsection{Talks}
\begin{cvhonors}
\cvhonor{Speaker - Evolutionary Motion Control Optimization in Physical Human-Robot Interaction}{2018 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}{}{2018-10}{}
\cvhonor{Speaker - Calibrating Robots with Python}{PyCon Canada 2017}{}{2017-11}{}
\cvhonor{Speaker - Calibrating Robots with Python}{Montréal-Python 67}{}{2017-10}{}
\cvhonor{Keynote - Robotics and Neuroscience}{Clearpoint Elementary Exhibition Summit}{}{2016-12}{}
\cvhonor{Speaker - Medical Robotics}{McGill Faculty of Medicine Explore Camp}{}{2015-06}{}
\cvhonor{Keynote}{Riverdale High School Career Seminar}{}{2014-05}{}
\cvhonor{Keynote}{Riverdale High School Career Seminar}{}{2014-02}{}
\cvhonor{Keynote}{Lester B. Pearson School Board Science Showcase}{}{2013-05}{}
\end{cvhonors}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\cvsection{Workshops}
\begin{cventries}
\cventry{MUSE 1.0 Bedside Ultrasound Course for Primary Care Clinicians}{McGill University Steinberg Centre for Simulation and Interactive Learning}{Montréal, Canada}{2017-01}{}
\cventry{Collaborative Robots Workshop}{RIA International}{Boston, U.S.}{2016-05}{}
\end{cventries}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\cvsection{Projects}
\begin{cventries}
\cventry{Team Coordinator and Electronics Designer - Formula SAE}{McGill Racing Team}{Montréal, Canada}{2010 - 2013}{}
\cventry{Mechanical Designer - Electricity-free Polymerase Chain Reaction (PCR) System}{McGill University Micro and NanoBioengineering Lab}{Montréal, Canada}{2013 - 2014}{}
\end{cventries}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\cvsection{Awards}
\begin{cvhonors}
\cvhonor{Alexander Graham Bell Canada Graduate Scholarship}{NSERC}{}{2015}{}
\cvhonor{Mitacs Accelerate Industrial Research Grant}{Mitacs}{}{2014}{}
\cvhonor{Graduation Honours}{McGill University}{}{2014}{}
\cvhonor{Québec Iron Titanium Scholarship}{McGill University}{}{2013}{}
\cvhonor{Abe and Jennie Brock Award}{McGill University}{}{2013}{}
\cvhonor{Dean's Honour List}{McGill University}{}{2013}{}
\cvhonor{Industrial Undergraduate Research Award}{NSERC}{}{2013}{}
\cvhonor{Industrial Undergraduate Research Award}{NSERC}{}{2012}{}
\cvhonor{Industrial Undergraduate Research Award}{NSERC}{}{2011}{}
\cvhonor{Golden Key International Honour Society}{McGill University}{}{2011}{}
\cvhonor{First Class Graduation Honours}{Dawson College}{}{2010}{}
\cvhonor{Athletic Academic Achievement Award}{Dawson College}{}{2010}{}
\end{cvhonors}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\cvsection{Certifications}
\begin{description}
\item[Professional Engineer (P.Eng.)] Ordre des ingénieurs du Québec (OIQ)
\item[Associate Value Specialist (AVS)] SAVE International
\item[Open Water Diver] Professional Association of Diving Instructors (PADI)
\end{description}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\end{document}