\cvsection{Work}
\begin{cventries}

\cventry
{Engineering Manager}
{AON3D}
{Montréal, Canada}
{2019 - }
{
\begin{cvitems}
\item{Head of software and hardware engineering, and member of executive team.}
\item{Oversee the design, development, testing, and deployment of innovative solutions for challenging problems in the additive manufacturing domain.}
\item{Ensure robust, scalable, reusable, efficient, production-quality software and hardware is being delivered to the organization.}
\item{Usher and evangelize adoption of engineering best-practices and agile methodologies.}
\item{Set the roadmap and budgets, drive detailed planning, and ensure execution of deliverables for a medium sized team.}
\item{Manage the company-wide SR\&ED program.}
\item{Mentor and help bringing up of new team members, interviewing and hiring of new team members, ensure technical development of team.}
\end{cvitems}
}

\cventry
{Senior R\&D Engineer}
{AON3D}
{Montréal, Canada}
{2018 - 2019}
{
\begin{cvitems}
\item{Responsible for innovation and technology development to drive 10x revenue.}
\item{Introduced automated data collection framework to help drive business and engineering decisions.}
\item{Engineering ScrumMaster, responsible for ensuring the team has everything they need to deliver value.}
\end{cvitems}
}

\cventry
{Technology Advisor to the CEO}
{YPC Technologies}
{Montréal, Canada}
{2017 - 2018}
{
\begin{cvitems}
\item{Advised CEO throughout FounderFuel startup accelerator in order to go to market and raise seed capital.}
\item{Led a team of engineers and directed robotics and software design, development, and implementation.}
\item{Recommended long-term approach to strategic suppliers and technologies with the aim of optimizing operations and delivering savings.}
\end{cvitems}
}

\cventry
{R\&D Engineer}
{Rogue Research Inc.}
{Montréal, Canada}
{2011 - 2018}
{
\begin{cvitems}
\item{Led mechanical research, design, and development of brain imaging, cognitive neuroscience, and robotic products.}
\item{Led the development of a novel robotic veterinary neurosurgery system, including trajectory generation algorithms, computer vision, and hardware design.}
\item{Developed devices and systems for transcranial magnetic stimulation (TMS), near infrared spectroscopy (NIRS), deep brain stimulation (DBS), and image-based neuronavigation.}
\end{cvitems}
}

\end{cventries}
