\cvsection{Recent Publications}
\begin{cvhonors}

    \cvhonor
    {Improved Test Methods for Polymer AM Inter-Layer Weld Strength and Filament Mechanical Properties}
    {Richard G. Cole, Kazem Fayazbakhsh, Abraham Avalos, Nicholas A. Nadeau. ASTM International Conference on Additive Manufacturing (ICAM).}
    {}
    {2020}

    \cvhonor
    {Towards the development of safe, collaborative robotic freehand ultrasound}
    {Nicholas A. Nadeau. École de technologie supérieure.}
    {}
    {2019}

    \cvhonor
    {Pybotics: Python Toolbox for Robotics}
    {Nicholas A. Nadeau. The Journal of Open Source Software.}
    {}
    {2019}

    \cvhonor
    {Impedance Control Self-Calibration of a Collaborative Robot Using Kinematic Coupling}
    {Nicholas A. Nadeau, Ilian A. Bonev. MDPI Robotics.}
    {}
    {2019}

    \cvhonor
    {Evolutionary Motion Control Optimization in Physical Human-Robot Interaction}
    {Nicholas A. Nadeau, Ilian A. Bonev. IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS).}
    {}
    {2018}

    \cvhonor
    {An Extrinsic Dexterity Approach to the IROS 2018 Fan Robotic Challenge Modality B}
    {Jennifer Kwiatkowski, Jean-Philippe Roberge, Nicholas A. Nadeau, Louis L'Écuyer-Lapierre, Vincent Duchaine. IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS).}
    {}
    {2018}

    \cvhonor
    {Characterization of a robotic micro-surgical system for small-animal neurosurgery}
    {Nicholas A. Nadeau, Alexandru Ciobanu, Fred Lamer, Mathieu Coursolle, Sean McBride, Stephen Frey, Roch Comeau. Society for Neuroscience.}
    {}
    {2017}

\end{cvhonors}
