\cvsection{Work}
\begin{cventries}

    \cventry
    {CTO}
    {Halodi Robotics}
    {Montréal, Canada \& Oslo, Norway}
    {2021 - }
    {
        \begin{cvitems}
            \item{Spearheaded the development of a new humanoid robot design for security guarding.}
            \item{Successful \href{https://www.halodi.com/press-releases/adt-invests-in-and-partners-with-halodi-robotics-lbz49}{Series A funding of \$10M with Valinor and ADT Commercial}.}
            \item{Led company \href{https://www.nicholasnadeau.com/talk/society-robots-and-us-hiring-for-inclusive-robotics/}{recruitment and growth} to 50+ employees in 4 countries.}
            \item{Led pilot projects with enterprise customers leading to the single biggest contract ever for humanoid robots (\href{https://www.halodi.com/press-releases/halodi-robotics-inks-contract-with-adt-commercial-for-delivery-of-140-humanoid-robots}{140 robots to ADT Commercial}).}
            \item{Led software development, team management, architecture design, and implementation of internal infrastructure.}
            \item{General manager of Halodi Robotics Canada Inc.}
        \end{cvitems}
    }

    \cventry
    {Advisor}
    {BRIDGR}
    {Montréal, Canada}
    {2020 - }
    {
        \begin{cvitems}
            \item{Expert advisor assisting with team growth, architecture, and special projects (e.g., robotics, Industry 4..0) and critical introductions.}
            \item{Mentor through the Techstars AI Montréal accelerator.}
        \end{cvitems}
    }

    \cventry
    {Engineering Manager}
    {AON3D}
    {Montréal, Canada}
    {2018 - 2021}
    {
        \begin{cvitems}
            \item{Head of engineering and executive team member through \href{https://techcrunch.com/2021/09/02/3d-printing-startup-aon3d-closes-11-5m-series-a/}{\$11.5M Series A with SineWave Ventures, AlleyCorp, and Y Combinator}.}
            \item{Led engineering team management, \href{https://www.nicholasnadeau.com/talk/making-materials-matter/}{software and hardware development}, \href{https://www.nicholasnadeau.com/talk/the-products-by-design-podcast/}{product direction}, and certification to develop \href{https://www.aon3d.com/}{high-performance 3D printing and additive manufacturing systems}.}
            \item{Responsible for Scientific Research and Experimental Development (SR\&ED) Tax Incentive Program (\$300K+ in tax refunds).}
        \end{cvitems}
    }

    \cventry
    {Founder}
    {Nadeau Innovations}
    {Montréal, Canada}
    {2017 - }
    {
        \begin{cvitems}
            \item{Provide fractional CTO services, technical development, roadmap planning and strategy, and team building support.}
        \end{cvitems}
    }

    \cventry
    {Technology Advisor to the CEO}
    {YPC Technologies}
    {Montréal, Canada}
    {2017 - 2018}
    {
        \begin{cvitems}
            \item{Advised CEO throughout FounderFuel startup accelerator, leading to a \href{https://www.ypc-technologies.com/ypc-seed-round-oct2020}{\$1.8M seed with Hike Ventures, Real Ventures, and Toyota AI Ventures}.}
            \item{Led a team of engineers and directed robotics and software design, development, and implementation for FounderFuel Demo Day.}
        \end{cvitems}
    }

    \cventry
    {R\&D Engineer}
    {Rogue Research Inc.}
    {Montréal, Canada}
    {2011 - 2018}
    {
        \begin{cvitems}
            \item{Led the development of a \href{https://www.nicholasnadeau.com/publication/nadeau-2017-characterization/?q=character}{novel robotic veterinary neurosurgery system}, including trajectory generation algorithms, computer vision, and hardware design.}
            \item{Developed \href{https://www.rogue-research.com/}{biomedical devices and systems} for transcranial magnetic stimulation (TMS), near-infrared spectroscopy (NIRS), deep brain stimulation (DBS), and image-based neuronavigation.}
        \end{cvitems}
    }

\end{cventries}
